---
title: "ch16-case2"
author: "Jackie Ocana"
date: "2/10/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Ch 16 Case 2 - Wine Ratings 
##Q1
Develop a table that shows the number of wines that were classified as classic, 
outstanding, very good, good, mediocre, and not recommended and the average price. 
Does there appear to be any relationship between the price of the wine and the 
Wine Spectator rating? Are there any other aspects of your initial summary of the
data that stand out?

```{r cars}
#set up data
rm(list = ls())
library("readxl")
wineratings <- read_excel("/Users/Jackie/Desktop/MSBA5504-advanced-data-analytics/data-files/wineratings.xlsx")

#show counts
table(wineratings$Rating)

#regression price and score
wineratings_mlr <- lm(Price ~ Score, data=wineratings)
summary(wineratings_mlr)
```

##Q2 
Develop a scatter diagram with price on the horizontal axis and the Wine 
Spectator score on the vertical axis. Does the relationship between price and 
score appear to be linear?

```{r pressure, echo=FALSE}
library(ggplot2)
ggplot(wineratings, aes(x = `Price`, y = `Score`)) +
  geom_point()
#The relationship does not appear to be linear. It appears to be curvilinear.
```

Q3
Using linear regression, develop an estimated regression equation that can be 
used to predict the score given the price of the wine.
```{r}
wineratings_mlr2 <- lm(Score ~ Price, data=wineratings)
summary(wineratings_mlr2)
#Score = 87.763226 + 0.027995x
```
Q4
Using a second-order model, develop an estimated regression equation that can be 
used to predict the score given the price of the wine.

```{r}
#t indicates polynomial model
#y=11785.9704+-278.4274x + 1.6450x^2
modelc <- lm(Price ~ poly(Score, 2, degree = 2, raw = T), data = wineratings)
summary(modelc)
```


Q5
Compare the results from fitting a linear model and fitting a second-order model.
```{r}
#The model in question 4 has a higher r squared indicating a stronger relationship 
#than the previous model
```


Q6
As an alternative to fitting a second-order model, fit a model using the natural
logarithm of price as the independent variable. Compare the results with the 
second-order model.
```{r}
#This is an even stronger relationship than with the previous model as r squared is 
#even higher
wineratings$LnPrice <-log(wineratings$Price)
modelln <- lm(LnPrice ~ Price, data = wineratings)
summary(modelln)
plot(modelln, which = 3)

```

Q7
Based upon your analysis, would you say that spending more for a bottle of wine 
will provide a better wine?
```{r}
#up until a certain point, yes it is a better wine, however, eventually it plateus,
#and the price does not make much of a difference.
```
Q8
Suppose that you want to spend a maximum of $30 for a bottle of wine. In this 
case, will spending closer to your upper limit for price result in a better wine
than a much lower price?
```{r}
#No, it will not result in a much better wine.

```

